Synthesizing Symmetric Lenses

### 2019-02-27 papers/SymmetricLenses/main.tex
update relevance annotations to be smoother text

We can solve both problems by allowing users to augment the specifications with
\emph{relevance annotations}. Sometimes, users have external knowledge that certain
information appears exclusively in one format or the other or conversely appears
in both formats. By communicating this knowledge to the synthesis algorithm
through relevance annotations, users can force the synthesis of lenses that
discard or retain certain information.
The first annotation, $\SkipOf{\Regex}$, says the information of
$\Regex$ appears only in $\Regex$, and can safely be
projected. The second annotation, $\SRequireOf{\Regex}$, says the information of
$\Regex$ appears in the other format and cannot be discarded.

@@

Our implementation includes a number of optimizations not described above:
annotations that guide DNF conversion; an expansion inference algorithm;
hash-consing and memoization; and compositional synthesis. The implementation
also provides for additional specifications in the form of annotations that help
describe which information is irrelevant to the lens. The optimizations make the
system performant enough for interactive use, and the annotations help ensure
the desired information is projected.

>>>>

We can solve both problems by allowing users to augment the specifications with
\emph{relevance annotations}. Sometimes, users have external knowledge that certain
information appears exclusively in one format or the other, or they may know the
information is present both formats. By communicating this knowledge to the synthesis algorithm
through relevance annotations, users can force the synthesis of lenses that
discard or retain certain information.
The first annotation, $\SkipOf{\Regex}$, says the information of
$\Regex$ appears only in $\Regex$, and can safely be
projected. The second annotation, $\SRequireOf{\Regex}$, says the information of
$\Regex$ appears in the other format and cannot be discarded.

@@

Our implementation includes a number of optimizations not described above:
annotations that guide DNF conversion; an expansion inference algorithm;
hash-consing and memoization; and compositional synthesis. The optimizations
make the system performant enough for interactive use, and the annotations help
ensure the desired information is projected.
